### 2020-11-22 latex/acrobot.tex
Small edit of the oscillation proof, and updated the draft pdf

Let \(x(0) \in \mathcal{O}_\epsilon \subset \mathcal{O}\).
Since \(\dot{\alpha} > 0\), the orbit \(x(t)\) spirals clockwise around
the origin.
If this orbit remains in \(\mathcal{O}\), it must intersect
the \(q_u\) axis at some radius \(\mu = \delta\)
which depends on the initial condition \(x(0)\).
Take 
\[
    \underbar{\delta} = 
    \min\limits_{x(0) \in \bar{\mathcal{O}}_\epsilon} \delta(x(0))
    ,
\] 
which exists because \(\bar{\mathcal{O}}_\epsilon\) is compact.
Fruthermore, \(\underbar{\delta} \leq \epsilon\).
From the previous perturbation analysis,
there exists \(I^\prime(\underbar{\delta})\) small enough that
\(P_\mathcal{O}(\mu_0)\) is positive for all 
\(\mu_0 \in [\underbar{\delta},\pi[\).

Suppose \(x(0) \in \mathcal{O}_\epsilon\), and the orbit
intersects the \(q_u\)-axis at some point \(x(t_0) = (u_0, 0)\).
The Poincar\'{e} section \(P_\mathcal{O}(|u_0|)\) is positive because 
\(|u_0| \geq \underbar{\delta}\).
As the acrobot continues its oscillation, it will intersect the \(q_u\) axis
again at a new point \(x(t_1) = (u_1,0)\).

Setting \(p_1 := P_\mathcal{O}(|u_0|)\),
Theorem \ref{thm:khalil-perturbation} guarantees that,
for all \(I \in ]0,I^\prime(\underbar{\delta})]\),
\[
    \abs{|u_1| - p_1} \leq cI^2
    ,
\]
where \(c > 0\) is an independent constant.
This implies that \(|u_1| \geq p_1 - cI^2\). 
We also know that
\[
    p_1 - |u_0| \geq IKQ(|u_0|) \geq IKQ(\underbar{\delta}) > 0
    .
\]
There exists \(I^\star \in ]0,I^\prime(\underbar{\delta})]\) where
\(c{I^\star}^2 < I^\star KQ(\underbar{\delta})\), which means
\begin{align*}
    |u_1| - |u_0| 
    &= \left(|u_1| - p_1\right) + \left(p_1 - |u_0|\right)
    \\
    &\geq \left(p_1 - c{I^\star}^2 - p_1\right) + I^\star KQ(\underbar{\delta})
    \\
    &= I^\star KQ(\underbar{\delta}) - c{I^\star}^2
    \\
    &> 0
    .
\end{align*}

Since \(u_0 \in [\underbar{\delta},\pi[\) was arbitrary, 
we can apply Theorem \ref{thm:khalil-perturbation} iteratively:
initializing the acrobot at \(x(t_i) = (u_i, 0)\), the
next intersection with the \(q_u\) axis will be at
\(x(t_{i+1}) = (u_{i+1},0)\) with \(|u_{i+1}| > |u_i|\).

Because the Poincar\'{e} section is monotonically increasing, 
the orbit will eventually reach an intersection point \(x(t_N) = (u_N,0)\)
such that \(P_\mathcal{O}(|u_N|) > \pi + c{I^\star}^2\). 
At this point, the orbit will no longer return to the
\(q_u\)-axis.
Instead, it will escape \(\mathcal{O}\) entirely; 
in doing so, it also escapes \(\mathcal{O}_\epsilon\).
Hence, the orbit must escape any compact subset of \(\mathcal{O}\) in finite
time. 
We conclude that the acrobot is gaining energy on \(\mathcal{O}_\epsilon\).

Setting \(I < 0\), the Poincar\'{e} section \(P_\mathcal{O}(\mu_0)\) is now
monotonically decreasing in \(\mu_0\).
By the same arguments presented in this section, the constraint 
must be dissipating energy.

>>>>

Let \(x(0) \in \mathcal{O}_\epsilon \subset \mathcal{O}\).
Since \(\dot{\alpha} > 0\), the orbit \(x(t)\) spirals clockwise around
the origin.
If this orbit remains in \(\mathcal{O}\), it must intersect
the \(q_u\) axis at some radius \(\mu = \delta\)
which depends on the initial condition \(x(0)\).
Take 
\[
    \underbar{\delta} = 
    \min\limits_{x(0) \in \bar{\mathcal{O}}_\epsilon} \delta(x(0))
    ,
\] 
which exists because \(\bar{\mathcal{O}}_\epsilon\) is compact.
Furthermore, \(\underbar{\delta} \leq \epsilon\) because
\(x(0) = (\epsilon,0) \in \bar{\mathcal{O}}_\epsilon\).
From the previous perturbation analysis,
there exists \(I^\prime(\underbar{\delta})\) small enough that
\(P_\mathcal{O}(\mu_0)\) is positive for all 
\(\mu_0 \in [\underbar{\delta},\pi[\).

Suppose \(x(0) \in \mathcal{O}_\epsilon\) and that the orbit
intersects the \(q_u\)-axis at some point \(x(t_0) = (u_0, 0)\), which
has pseudo-radius \(\mu = \abs{u_0}\).
The Poincar\'{e} section \(P_\mathcal{O}(\abs{u_0})\) is positive because 
\(\abs{u_0} \geq \underbar{\delta}\).
As the acrobot continues its oscillation, it will intersect the \(q_u\) axis
again at a new point \(x(t_1) = (u_1,0)\).

Setting \(p_1 := P_\mathcal{O}(\abs{u_0})\),
Theorem \ref{thm:khalil-perturbation} guarantees that,
for all \(I \in ]0,I^\prime(\underbar{\delta})]\),
\[
    \abs{\abs{u_1} - p_1} \leq cI^2
    ,
\]
where \(c > 0\) is an independent constant.
This implies that \(\abs{u_1} \geq p_1 - cI^2\). 
We also know that
\[
    p_1 - \abs{u_0} \geq IKQ(\abs{u_0}) \geq IKQ(\underbar{\delta}) > 0
    .
\]
There exists \(I^\star \in ]0,I^\prime(\underbar{\delta})]\) where
\(c{I^\star}^2 < I^\star KQ(\underbar{\delta})\), which means
\begin{align*}
    \abs{u_1} - \abs{u_0} 
    &= \left(\abs{u_1} - p_1\right) + \left(p_1 - \abs{u_0}\right)
    \\
    &\geq \left(p_1 - c{I^\star}^2 - p_1\right) + I^\star KQ(\underbar{\delta})
    \\
    &= I^\star KQ(\underbar{\delta}) - c{I^\star}^2
    \\
    &> 0
    .
\end{align*}

Since \(u_0 \in [\underbar{\delta},\pi[\) was arbitrary, 
we can apply Theorem \ref{thm:khalil-perturbation} iteratively:
initializing the acrobot at \(x(t_i) = (u_i, 0)\), the
next intersection with the \(q_u\) axis will be at
\(x(t_{i+1}) = (u_{i+1},0)\) with \(\abs{u_{i+1}} > \abs{u_i}\).

Because the Poincar\'{e} section is monotonically increasing, 
the orbit will eventually reach an intersection point \(x(t_N) = (u_N,0)\)
such that \(P_\mathcal{O}(\abs{u_N}) > \pi + c{I^\star}^2\). 
At this point, the orbit will no longer return to the
\(q_u\)-axis.
Instead, it will escape \(\mathcal{O}\) entirely, which means
it also escapes \(\mathcal{O}_\epsilon\).
Hence, the orbit must escape any compact subset of 
\(\mathcal{O}_\epsilon\) in finite time. 
We conclude that the acrobot is gaining energy on \(\mathcal{O}_\epsilon\).

Setting \(I < 0\), the Poincar\'{e} section \(P_\mathcal{O}(\mu_0)\) is now
monotonically decreasing in \(\mu_0\).
By the same arguments presented in this section, the constraint 
must be dissipating energy on \(\mathcal{O}_\epsilon\).
